% Main file for the GREIT Algorithm
% $Id$
\documentclass[12pt]{iopart}
\usepackage{graphicx}
 \usepackage{amssymb}
 \usepackage{amsbsy}
\newcommand{\vB}{\mbox{$\mathbf{v}$}}
\newcommand{\xB}{\mbox{$\mathbf{x}$}}
\newcommand{\xH}{\mbox{$\mathbf{\hat x}$}}
\newcommand{\xT}{\mbox{$\mathbf{\tilde x}$}}
\newcommand{\XT}{\mbox{$\mathbf{\tilde X}$}}
\newcommand{\nB}{\mbox{$\mathbf{n}$}}
\newcommand{\yB}{\mbox{$\mathbf{y}$}}
\newcommand{\wB}{\mbox{$\mathbf{w}$}}
\newcommand{\AB}{\mbox{$\mathbf{A}$}}
\newcommand{\BB}{\mbox{$\mathbf{B}$}}
\newcommand{\RB}{\mbox{$\mathbf{R}$}}
\newcommand{\IB}{\mbox{$\mathbf{I}$}}
\newcommand{\JB}{\mbox{$\mathbf{J}$}}
\renewcommand{\PB}{\mbox{$\mathbf{P}$}}
\newcommand{\VB}{\mbox{$\mathbf{V}$}}
\newcommand{\WB}{\mbox{$\mathbf{W}$}}
\newcommand{\XB}{\mbox{$\mathbf{X}$}}
\newcommand{\YB}{\mbox{$\mathbf{Y}$}}
% Use boldsymbol when using amssymb
 \newcommand{\SG}{\mbox{${\boldsymbol \Sigma}$}}
 \newcommand{\TG}{\mbox{${\boldsymbol \Theta}$}}
 \newcommand{\sG}{\mbox{${\boldsymbol \sigma}$}}
%\newcommand{\SG}{\mbox{${\mathbf \Sigma}$}}
%\newcommand{\TG}{\mbox{${\mathbf \Theta}$}}
%\newcommand{\sG}{\mbox{${\mathbf \sigma}$}}
\newcommand{\SNR}{\mbox{\small $\mathrm{SNR }$}}
\newcommand{\NF}{\mbox{\small $\mathrm{NF }$}}
\newcommand{\EIT}{\mbox{\small $\mathit{EIT }$}}
\begin{document}

\title[FEM variability and EIT images]{%
 Compensating for EIT image reconstruction errors due to 
   FEM variability 
}
%{\small \tt DRAFT: $Date$}

\author{Andy Adler$^{1}$,
        William R B Lionheart$^{2}$,
       }

\address{ $^{1}$Systems and Computer Engineering,
                Carleton University, Ottawa, Canada}
\address{$^{13}$School of Mathematics, University of Manchester, UK}



\begin{abstract}
Electrical Impedance Tomography (EIT)
\end{abstract}

\noindent{\it Keywords\/}:
Electrical Impedance Tomography,
Image Reconstruction,
Finite Element Models

\section{Introduction}
Electrical Impedance Tomography (EIT) measures conductivity
changes within a body, by measuring the voltages at electrodes
on the body surface caused when a number of different
currents are passed through the body.



\References % Harvard style references
\item[]
Adler A and Guardo R 1996 Electrical impedance tomography:
regularized imaging and contrast detection {\em IEEE Trans. Med.
Imaging} {\bf 15} 170-179

\item[]
Adler A, Guardo R and Berthiaume Y 1996 Impedance imaging of lung
ventilation: Do we need to account for chest expansion? {\em IEEE
Trans. Biomed. Eng.} {\bf 43}(4) 414-20


\item[]
Adler A and Lionheart W R B 2006
Uses and abuses of EIDORS: An extensible software base for EIT
{\em Physiol Meas}
27 S25--S42

%\item[]
%Barber D C
%Brown B H
%Freeston I L, 1983
%Imaging spatial distributions of resistivity using applied potential tomography
%{\em Electronics Letters}
%19 933--935
%

\item[]
Barber D C and Brown B H 1984
Applied potential tomography
{\em J Phys E: Sci Instrum}
 17 723--733

\item[]
Barber D C and Brown B H 1988 Errors in reconstruction of
resistivity images using a linear reconstruction technique {\em
Clin. Phys. Physiol. Meas.} 
9(suppl. A) 101--4

\item[]
Barber D C 1989
A review of image reconstruction techniques for electrical
 impedance tomography
{\em Med Phys}
16 162--169


\item[]
Brown B W 2003
Electrical impedance tomography (EIT): a review
{\em J Medical Eng. \& Technology}
27 97--108


\item[]
Cheney M, Isaacson D, Newell J C, Simske S and Goble J C 1990
NOSER: an algorithm for solving the inverse conductivity problem
{\em Int J Imaging Syst Technol} 
2 66--75

\item[]
Cheng KS, Newell JC, Gisser DG, 1989
Electrode Models for Electric Current Computed Tomography
{\em IEEE Trans in Biomedical Eng}
36 918--924

\item[]
G\'omez-Laberge C Adler A 2008
Direct EIT Jacobian calculations for conductivity change and electrode movement
{\em Physiol Meas}
29 S89--S99


\item[]
Hahn G Just A Dittmar J  Hellige G 2008
Systematic errors of EIT systems determined by easily-scalable
 resistive phantoms
{\em Physiol Meas}
 29 S163--S172
 
\item[]
Lionheart W R B 2004
EIT reconstruction algorithms: pitfalls, challenges
and recent developments
{\em Physiol Meas}
25 125--142

\item[]
Oh S, Tang T, Sadleir R 2007
Quantitative analysis of shape change in Electrical Impedance Tomography (EIT)
in {\em IFMBE Proceedings}
17 424--427

\item[]
Polydorides N and Lionheart W R B 2002 A Matlab toolkit for
three-dimensional electrical impedance tomography: A contribution
to the Electrical Impedance and Diffuse Optical Reconstruction
Software project {\em Meas Sci Technol} {\bf 13} 1871-83

\item[]
Schoberl J 1997
NETGEN: An advancing front 2D/3D-mesh generator based on abstract rules
{\em Computing and Visualization in Science}
1 41--52 

\item[]
Soleimani M, G\'omez-Laberge C and Adler A 2006 Imaging of
conductivity changes and electrode movement in EIT
{\em Physiol Meas} {\bf 27}
S103--S13

\item[]
Tizzard A Horesh L Yerworth R J Holder D S Bayford R H 2005
Generating accurate finite element meshes for the forward
model of the human head in EIT
{\em Physiol Meas}
 26 S251--61 

\item[]
Yorkey T J, Webster J G and Tompkins W J 1987
Comparing reconstruction algorithms for electrical
impedance tomography
{\em IEEE Trans. Biomed. Eng}
34 843--52


\endrefs

\end{document}
